Everything you wanted to know about PanDA but were truly truly afraid to ask

### 2017-03-11 nge.tex
Transition V to VI

As seen in \S\ref{sec:panda_deployment}, PanDA Broker has been designed to
submit PBS jobs to Titan's batch system instead of pilots due to the absence of
wide area network connectivity on Titan's work nodes. As discussed in
\S\ref{sec:panda_titan}, the unavailability of pilots imposes three main
limitations: (i) static coupling between PBS jobs and detector simulations and
(ii) support for a single type of payload.

@@

The support of workload generations would enable a more efficient use of the
backfill availability walltime. Currently, when a set of simulations ends also
the PBS ends, independently on whether more walltime would still be available.
With a pilot, more simulations could be executed so to utilize all the walltime
while avoiding further job packaging and submission overheads.\mtnote{more?}

Pilots offer a general scheduling interface while hiding the mechanics of
coordinating resources across multiple work nodes. This eliminates the need of
packaging payload into PBS jobs within the broker, greatly simplifying the
submission process. This simplification would make it possible to submit
different types of payload without having to develop a specific PBS script for
every payload.

>>>>

As seen in \S\ref{sec:panda_deployment}, the absence of wide area network
connectivity on Titan's work nodes was one of the main reasons for PanDA Broker
not to implement pilots. As discussed in \S\ref{sec:panda_titan}, the absence of
pilots imposes the static coupling between PBS jobs and detector simulations,
and development tailored to each type of payload that needs to be executed.

@@

The support of workload generations would enable a more efficient use of the
backfill availability walltime. Currently, when a set of simulations ends also
the PBS job ends, independently on whether more walltime would still be
available. With a pilot, more simulations could be executed so to utilize all
the available walltime, while avoiding further job packaging and submission
overheads.\mtnote{Are there more reasons for wanting multiple generations?}

Pilots can offer a payload-independent scheduling interface while hiding the
mechanics of coordination and communication among multiple work nodes. This
could eliminate the need for packaging payload into PBS jobs within the broker,
greatly simplifying the submission process. This simplification would also
enable the submission of different types of payload, without having to develop a
specific PBS script for every payload. Finally, the submission process would be
MPI-independent, as MPI is used for coordination among multiple work nodes, not
by the payload.

\mtnote{NOTE: I do not mention backfill availability Vs normal availability (i.e., submitting to the queue a `normal' job) because, in theory, the design of PanDA Broker enable this capability. I would speak about about backfill/not backfill in the discussion of NGE, when speaking about its generality. Part of this generality, is being able to submit to whatever batch system is supported by SAGA, including Titan's PBS and all its queues.}

\mtnote{NOTE: NGE is not able to use backfill on Titan as we do not have specific functionalities to interrogate the Moab scheduler about backfill availability. This is why NGE should be presented as the pilot for PanDA Broker and not as an alternative to PanDA Broker. NGE alone would not be able to speak directly to PanDA Server.}

% -----------------------------------------------------------------------------
\subsection{Next Generation Executer}
\label{ssec:nge}

\begin{enumerate}
    \item Rationale and design (why)
    \item Architecture (how)
    \item Integration
    \item Characterization (experiments)
\end{enumerate}

We are developing a prototype of Next Generation Executer (NGE) to add pilot
capabilities to the PanDA Broker. NGE is \ldots
